Modelling BCG vaccination in the UK

### 2019-04-30 index/08-model-development.Rmd
fixed thesis building in correct format (without packrat

```{r summary-scenarios, results = "asis"}
scenarios <- tibble(
  Parameter = c("$\beta_a$ - transmission probability", "", ""),
  Scenario = c("*Constant across age groups*",
               "Variable between children (0-14) and adults (15-89)",
               "Variable between children (0-14), adults (15-59), and older adults (60-80)")
) %>% 
  add_row(
    Parameter = c("Historic non-UK born cases", "", ""),
    Scenario = c("*Linear increase from 1960 to 1999 based on notifications in 2000*",
                 "Increasing from 1960 to 1999 based on notifications in 2000 using a log link function.")
  )

pander(scenarios, caption = "(\\#tab:summary-scenarios) Summary of planned scenario analyses to be carried out in the next chapter as part of model fitting by comparision of the goodness of fit to the data. The baseline scenarios are indicated using italics.", split.cells = c(1, 20, 60), split.table = 100)
```

>>>>

```{r summary-scenarios}
scenarios <- tibble(
  Parameter = c("$\\beta_a$ - transmission probability", "", ""),
  Scenario = c("Constant across age groups",
               "Variable between children (0-14) and adults (15-89)",
               "Variable between children (0-14), adults (15-59), and older adults (60-80)")
) %>% 
  add_row(
    Parameter = c("Historic non-UK born cases", "", ""),
    Scenario = c("Increasing from 1960 to 1999 based on notifications in 2000 using a log link function.",
                 "Linear increase from 1960 to 1999 based on notifications in 2000",
                 ""
                 )
  )

kable(scenarios, caption = "Summary of planned scenario analyses to be carried out in the next chapter as part of model fitting by comparision of the goodness of fit to the data.", booktabs = TRUE, escape = FALSE) %>% 
  column_spec(c(1), width = "2cm") %>% 
  column_spec(c(2), width = "8cm")
```
